%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{CPAC Systems | Android Developer, Site Operations} % Job title
	{Kotlin, Java, TypeScript, SQL, Jenkins, Gerrit, Gradle, GraphQL, gRPC, XML, Jetpack Compose, Room, Azure DevOps, JUnit/Truth, MockK}
	{Göteborg} % Location
	{Feb. 2025 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Built Android functionality for Volvo Site Operations, integrating Dig Assist, Load Assist and Haul Assist with machine and operator workflows.}
			\item {Expanded Volvo cloud integration, connecting more data and workflows to backend systems.}
			\item {Introduced Jetpack Compose and maintained a shared UI library to improve consistency and reuse across multiple apps.}
			\item {Served as architect for multiple projects, leading implementation direction and guiding the team to practical, successful solutions.}
			\item {Modernized architecture and engineering practices across the app suite to improve maintainability.}
			\item {Frequently acted as the engineering point of contact with PMs and customers, answering questions and finding solutions.}
			\item {Analyzed development workflows to identify recurring process bottlenecks and quality risks, driving improvements in review, testing, and engineering practices.}
		\end{cvitems}
	}
	\cventry 
	{Vector Informatik | Embedded Software Engineer} % Job title
	{C++, MISRA, Python, Java, DevOps, Docker, AUTOSAR, DoIP, TCP/TLS, UDP, IP} % Organization
	{Göteborg} % Location
	{Mar. 2024 - Feb. 2025} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented Adaptive AUTOSAR DoIP functionality in C++, writing code for the protocol and ensuring it integrated reliably with the in-vehicle network.}
			\item {Worked as part of a team responsible for 3–4 components across ASIL B to ASIL D, balancing safety, robustness and customer integration needs.}
			\item {Led a small improvement project to reduce heap allocation and speed startup for customers, and shared the resulting toolkit and best practices with the team.}
			\item {Co-owned one AUTOSAR component and joined customer discussions to ensure new features and bug fixes met expectations.}
		\end{cvitems}
	}

	\cventry
	{Knowit | DevOps Master's thesis} % Job title
	{DevOps, GitHub Actions, Gitlab CI/CD, Jenkins, Azure, Docker} % Organization
	{Linköping} % Location
	{Aug. 2023 - Dec. 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented a standardized DevOps workflow to address knowledge loss in project-based environments with high developer turnover}
			\item {Applied testing standards, coding standards, and containerization to enhance knowledge retention}
			\item {Automated workflows and integrated tools within a CI/CD pipeline for continuous delivery and process improvement}
			\item {Used CMMI (Capability Maturity Model Integration) to assess and define the organization’s DevOps maturity levels before and after}
		\end{cvitems}
	}

	\cventry
	{Maxar Technologies | Full stack Developer} % Job title
	{TypeScript, Python, React, Django, PostgreSQL, CesiumJS, GIS, Agile} % Organization
	{Linköping} % Location
	{Jun. 2023 - Aug. 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Built a web application from scratch to visualize data on an interactive globe.}
			\item {Handled the full development process as the sole developer, from gathering requirements based on team needs to implementing the solution.}
			\item {Worked using agile methods, delivering continuous updates and improvements on a weekly basis.}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}
